\textls[-0]{\thetitle}

### 2023-03-23 metatheory-condensed.tex
notation for field projection

We use \cref{fig:stlc-linkage-typing} to illustrate.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{%
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i}(-0.02,-0.10)(-0.02,0.28)
\mathit{self} : A_i%
\tikzmarkend{A-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i}%
}$.
%
The context types $A_i$ are a dependent tuple type, but for readability,
we write them as dependent record types that give labels to the fields.
%we use a notation with explicit names
%in this typing judgment:
%we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
%and write its type~$A_i$, which is a dependent tuple type, as a
%dependent record type with labels.
%
\begin{itemize}
% [leftmargin=4ex,itemsep=.5ex]
  [labelsep=*,leftmargin=1pc,itemsep=3pt]

@@

\item 
The next four fields model the four constructors of~\lsti{tm}.
Constructor \lsti{tm_unit} is modeled as $\Wsup{}{\wsig_{\texttt{tm}}}{\top}{x.\bot}$
and typed with $\El{\mathit{self}."tm"}$, where $\mathit{self}$ stands for
the typing context containing the first field~\lsti{tm}.
The W-type signature $\wsig_{\texttt{tm}}$ is exposed in
this typing context; that is, $\mathit{self}."tm"$ has type $\TyS{\wcode{\wsig_{\texttt{tm}}}}$.
So $\El{\mathit{self}."tm"}$ and $\El{\wcode{\wsig_{\texttt{tm}}}}$ can be equated,
as required by rule \ruleref{tm/wsup}.

>>>>

We use \cref{fig:stlc-linkage-typing} to illustrate.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{%
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i}(-0.02,-0.10)(-0.02,0.28)
\mathit{self} : A_i%
\tikzmarkend{A-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i}%
}$.
%
The context types $A_i$ are a dependent tuple type, but for readability,
we write them as dependent record types that give labels to the fields.
Field accesses are notated, for example, $\getfield{\mathit{self}}{"tm"}$.
%we use a notation with explicit names
%in this typing judgment:
%we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
%and write its type~$A_i$, which is a dependent tuple type, as a
%dependent record type with labels.
%
\begin{itemize}
% [leftmargin=4ex,itemsep=.5ex]
  [labelsep=*,leftmargin=1pc,itemsep=3pt]

@@

\item 
The next four fields model the four constructors of~\lsti{tm}.
Constructor \lsti{tm_unit} is modeled as $\Wsup{}{\wsig_{\texttt{tm}}}{\top}{x.\bot}$
and has type $\El{\getfield{\mathit{self}}{"tm"}}$, where $\mathit{self}$ stands for
the typing context containing the first field~\lsti{tm}.
The W-type signature $\wsig_{\texttt{tm}}$ is exposed in
this typing context; that is, $\getfield{\mathit{self}}{"tm"}$ has type $\TyS{\wcode{\wsig_{\texttt{tm}}}}$.
So $\El{\getfield{\mathit{self}}{"tm"}}$ and $\El{\wcode{\wsig_{\texttt{tm}}}}$ can be equated,
as required by rule \ruleref{tm/wsup}.

### 2023-03-23 stlc-linkage-typing-named.tex
notation for field projection

    \El{\mathit{self.}\texttt{tm}}

@@

            \El{\mathit{self}.\texttt{tm}} \to

@@

            \mathit{id} \to \El{\mathit{self}.\texttt{tm}}

@@

    \lambda t.\,\Wrec{\wsig_{\texttt{tm}}}{\dadada}{t}

@@

  $\TyTkg{\lsig_6} = \nTySigma{P_5}{\TyTkg{\lsig_5}}{\CaseSig{\top}{\bot}{\El{P_5.tm} \to \mathit{id} \to \El{P_5.tm}}}$\EDJ{It strike me that, we don't have field projection for dependent tuple... so it is a bit ambiguous. I am not sure if I should continue; but some explanation of this field projection is required I believe} & \\ 

>>>>

    \El{\getfield{\mathit{self}}{\texttt{tm}}}

@@

            \El{\getfield{\mathit{self}}{\texttt{tm}}} \to

@@

            \mathit{id} \to \El{\getfield{\mathit{self}}{\texttt{tm}}}

@@

    \lambda x.\,\Wrec{\wsig_{\texttt{tm}}}{\dadada}{x}

@@

  $\TyTkg{\lsig_6} = \nTySigma{P_5}{\TyTkg{\lsig_5}}{\CaseSig{\top}{\bot}{\El{\getfield{P_5}{"tm"}} \to \mathit{id} \to \El{\getfield{P_5}{"tm"}}}}$\EDJ{It strike me that, we don't have field projection for dependent tuple... so it is a bit ambiguous. I am not sure if I should continue; but some explanation of this field projection is required I believe} & \\ 
